Manuscript Figures for Genome Biology (simulation subset)

### 2018-09-07 manuscript_figures/manuscript_figures_sims.Rmd
Change sim plot y-axis format slightly

```{r genplot-function}
genplot <- function(tab, cov, type = c("info", "diff"), xt = "", met = c("FDR", "TPR"), ebw = 0.0025) {
    met <- match.arg(met)
    cov <- rlang::enquo(cov)
    type <- match.arg(type)
    if (type == "info") {
        ymean <- rlang::quo(mean.info)
        yse <- rlang::quo(se.info)
    } else if (type == "diff") {
        ymean <- rlang::quo(mean.diff)
        yse <- rlang::quo(se.diff)
    }        
    gp <- dplyr::filter(tab, key == met) %>%
        ggplot(aes(x = !!cov, y = !!ymean, color = Method, group = Method)) +
        geom_line(aes(linetype = Method), alpha = 0.85) +
        geom_errorbar(aes(ymin = !!ymean - !!yse, ymax = !!ymean + !!yse), width = ebw, alpha=0.5) +
        scale_linetype_manual(values = lty) + 
        scale_color_manual(values = col) +
        expand_limits(y = 0) +
        theme_classic() +
        theme(axis.title = element_text(face = "bold", size = 10),
              plot.title = element_text(face = "bold", size = 14))
    if (type == "diff") {
        gp <- gp + geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2)
        gp <- gp + scale_y_continuous(bquote(atop(Mean ~ Delta ~ .(met), (informative-uninformative))),
                                      labels = scales::percent)
    } else {
        gp <- gp + scale_y_continuous(met, labels = scales::percent)
        if (met == "FDR") {
            if (rlang::quo_name(cov) == "alpha") {
                gp <- gp + geom_abline(lty = 2, color = "blue", alpha = 1/2) 
            } else {
                gp <- gp + geom_hline(yintercept = 0.05, lty = 2, color = "blue", alpha = 1/2) 
            }
        }
    }
    gp
}
```

@@

## SFigure Sim4 C,D: FDR/TPR difference of methods
ps4c <- genplot(adaptmet, cov = alpha, type = "diff", met = "FDR") +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0)
ps4d <- genplot(adaptmet, cov = alpha, type = "diff", met = "TPR") +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0)

>>>>

```{r genplot-function}
genplot <- function(tab, cov, type = c("info", "diff"), xt = "", met = c("FDR", "TPR"), ebw = 0.0025) {
    met <- match.arg(met)
    cov <- rlang::enquo(cov)
    type <- match.arg(type)
    if (type == "info") {
        ymean <- rlang::quo(mean.info)
        yse <- rlang::quo(se.info)
    } else if (type == "diff") {
        ymean <- rlang::quo(mean.diff)
        yse <- rlang::quo(se.diff)
    }        
    gp <- dplyr::filter(tab, key == met) %>%
        ggplot(aes(x = !!cov, y = !!ymean, color = Method, group = Method)) +
        geom_line(aes(linetype = Method), alpha = 0.85) +
        geom_errorbar(aes(ymin = !!ymean - !!yse, ymax = !!ymean + !!yse), width = ebw, alpha=0.5) +
        scale_linetype_manual(values = lty) + 
        scale_color_manual(values = col) +
        expand_limits(y = 0) +
        theme_classic() +
        theme(axis.title = element_text(face = "bold", size = 10),
              plot.title = element_text(face = "bold", size = 14))
    if (type == "diff") {
        gp <- gp + geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2)
        gp <- gp + scale_y_continuous(bquote(Delta ~ .(met) ~ (informative-uninformative)),
                                      labels = scales::percent)
    } else {
        gp <- gp + scale_y_continuous(met, labels = scales::percent)
        if (met == "FDR") {
            if (rlang::quo_name(cov) == "alpha") {
                gp <- gp + geom_abline(lty = 2, color = "blue", alpha = 1/2) 
            } else {
                gp <- gp + geom_hline(yintercept = 0.05, lty = 2, color = "blue", alpha = 1/2) 
            }
        }
    }
    gp
}
```

@@

## SFigure Sim4 C,D: FDR/TPR difference of methods
ps4c <- genplot(adaptmet, cov = alpha, type = "diff", met = "FDR") +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0) +
    theme(axis.title.y = element_text(face = "bold", size = 9))
ps4d <- genplot(adaptmet, cov = alpha, type = "diff", met = "TPR") +
    scale_x_continuous(breaks = seq(0, .1, .02)) +
    expand_limits(x = 0) +
    theme(axis.title.y = element_text(face = "bold", size = 9))
